Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-08 mu/article/article.tex
Starting description when spin is fixed

@@

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
% 
\begin{table}[t]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
             &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
             &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
             &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
 CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
 GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\end{tabular}

\caption{\color{red} Comparison of the reported maxima values of
$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
polarization angle $\alpha$ and energy values.}
\label{tab:vab-str-comp}
\end{table}
} % COLOR RED END

@@

% \subsection{Fixing spin} % (fold)
% \label{sec:res-fixspin}

% \blindtext

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% \begin{figure}[t]
%     \centering
%     \subfigure[\, \label{fig:up-vaz-rag-1}]
%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
%     \\
%     \subfigure[\, \label{fig:up-vaz-rag-2}]
%     {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
%     \emph{up} structure.}
%     \label{fig:up-vaz-rag}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
%     \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|$ response for the
%     \emph{alt} structure.}
%     \label{fig:figure1}
% \end{figure}

% \blindtext

@@

    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The absolute maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
    range from 0.07\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
In Fig. \ref{fig:up-3d-vva-1} we present the
$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %% files: 
% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%

>>>>

\begin{table}[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{up}    & 2D   & 40    & 0.09  & $\mathrm{yz}$ &  87.16    \\
             &      &       & 1.94  & $\mathrm{yz}$ &  22.22    \\
             &      &       & 1.97  & $\mathrm{yz}$ & -29.70    \\
\emph{alt}   & 2D   & 145   & 0.72  & $\mathrm{yz}$ & -40.21    \\
             &      &       & 0.91  & $\mathrm{yz}$ & -32.89    \\
 CdSe        & bulk & 90    & 0.91  & $\mathrm{zz}$ & -26.87    \\
 GaAs        & bulk & 90    & 2.31  & $\mathrm{xx}$ & -21.62    \\
\hline
\end{tabular}

\caption{\color{red} Comparison of the reported maxima values of
$\mathcal{V}^{\mathrm{ab}}$ for different structures and the corresponding
polarization angle $\alpha$ and energy values.}
\label{tab:vab-str-comp}
\end{table}

@@

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk structures. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the terahertz radiation and reaching a
spin velocity of 87.16\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV all the
four structures have contributions in the same order of magnitude. 
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and reaching a
spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
% 
} % COLOR RED END

@@

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Up  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[t]
    \centering
    \subfigure[\ \label{fig:up-3d-vsz-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}}
    \\
    \subfigure[\ \label{fig:up-3d-vsz-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}}

    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
    structure for two energy ranges. The absolute maxima is located for an
    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vsz}
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[\, \label{fig:up-vaz-rag-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}}
    \\
    \subfigure[\, \label{fig:up-vaz-rag-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}}

    \caption{\color{red} Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
    figs (a) and (b)), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
    (circled box) and perpendicular (square box) angles, and the two components
    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
    }
    \label{fig:up-vaz-rag}
\end{figure}

We first present two energy ranges for the \emph{up} structure, the first for an
incoming energy beam from 0.0\,eV to 0.2\,eV where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV where two local maxima are
found.
% 
In Fig. \ref{fig:up-3d-vsz} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
the Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in the
Eq. \eqref{eq:vab} for the \emph{up} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we obtained that the zone where the maximum response is held
corresponds to a energy range of the incident beam from 0.084\,eV to 0.093\,eV
and polarization angles $\alpha$ between $30^{\circ}$ and $45^{\circ}$. Also two
local maxima are held for same polarization angles but for an energy range of
the incoming beam between 1.90\,eV and 2.05\,eV.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixing spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{\color{red} $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frame, left scale) the
    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
    scale), the collinear (circled box) and perpendicular (square box) angles,
    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:figure1}
\end{figure}

@@

    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The absolute maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

@@

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% 
In Fig. \ref{fig:up-3d-vva-1} we present the
$|\mathcal{V}^{\mathrm{a}}|(\omega)$ spectra resulting from evaluate the Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in the Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %% files: 
% %% vab-rtp.sm_0.03_x_12802_40-spin_scissor_0_Nc_32_ang_040
% %% vab-rtp.sm_0.03_y_12802_40-spin_scissor_0_Nc_32_ang_040
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
